### 2020-05-29 report/sections/evalconcl/eval.tex
Report:  theory section scaffolding
Report: section notes
Report: notes on part 3

\chapter{Evaluation}
%benchmark -- compile time / benchmarking

>>>>

\chapter{Evaluation}
\label{chap:eval}
%benchmark -- compile time / benchmarking

\section{Binary Sessions: \fancyname{Calculator}}
\begin{itemize}
\item sample client implementation + snippet of generated code (full in appendix)
\item show that not all the UI is being controlled by the runtime (i.e. calculator app has a header/fake navbar)
\item show the calculator logic achievable using React Context
\item sample server implementation + snippet of generated code (full in appendix)
\end{itemize}

\section{Multiparty Sessions: \fancyname{Noughts and Crosses}}
\begin{itemize}
\item sample client implementation -- show the flexibility of factory API for sending to be used in the UI part (since move selection can be be made )
\end{itemize}

\section{Routed Multiparty Sessions: \fancyname{Two Buyers}}
\begin{itemize}
\item show that the routing aspect is transparent to both sides
\end{itemize}

\section{Benchmarks}
\begin{itemize}
\item compile time: \begin{itemize}
\item use the examples from above to compare compilation time
\end{itemize}
\item execution time: based on parameterised ping pong with n messages
\begin{itemize}
\item n = 10, 100, 1000
\item benchmark using node timer tools in the backend as it knows when the protocol ends
\end{itemize}
\end{itemize}
